A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-07 paper/ms.tex
update ms

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster using kinematic information from Gaia, stellar rotation
  periods from TESS, and Li abundances from ground-based spectra.  To
  our knowledge, Kepler\,1627Ab is the youngest planet with a precise
  age yet found by the main Kepler mission.  From unresolved
  starspot-crossing events in the Kepler photometry and
  a Keck/HIRES transit we find that the planet is likely on an
  orbit aligned with the stellar spin axis.  We also briefly explore the flare
  arrival time distribution in the short cadence Kepler
  photometry.
  The $\delta$~Lyr cluster is one of many stellar groups whose
  properties have been clarified using the Gaia data; many other new
  clusters also overlap with confirmed and candidate exoplanets.
  Verifying the results of Gaia clustering analyses using TESS rotation
  periods seems likely to be an effective path toward expanding the census of
  age-dated planets, and our understanding of planetary evolution.
\end{abstract}

@@

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet
\citep[see {\it e.g.},]{soderblom_ages_2014}.
We acquired an iodine-free spectrum from
Keck/HIRES on the night of 26 March 2021 using the standard setup and
reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we find ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   Note that this value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Given the stellar
parameters of \sn\ (Table~\ref{tab:starparams}), most notably its
effective temperature, this measurement is also in agreement with an
age for the star between 30\,Myr and 50\,Myr ({\it e.g.}, 
\citealt{randich_gaiaeso_2018}; \citealt{bouma_2021_ngc2516}).

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.9\textwidth]{f4.pdf}
		}

		\subfloat{
			\includegraphics[width=0.87\textwidth]{f5.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
    30 minute cadence.  A one hundred day segment is shown here.  The
    {\it top panel} shows the \texttt{PDCSAP} median-subtracted flux
    in units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The model for the stellar
    variability (orange line) is subtracted below, revealing the
    transits of \pn, as well as other deviations from the stellar
    variability model.  The Figure Set available online shows the
    entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627b, with stellar variability
    removed.  The 2-$\sigma$ model uncertainties and the maximum {\it
    a posteriori} model are shown as the faint purple band, and the
    dark purple line.  Gray points are individual \texttt{PDCSAP} flux
    measurements; black points are binned to 20 minutes, with a
    representative error bar shown.  The asymmetric residual visible
    during the transit is robust against detrending methods; we
    believe it is caused by starspot crossings.
    \label{fig:lc}
  }
\end{figure*}

@@

If the \pn\ transit signal is created by a bonafide planet,  then to
our knowledge its age would make it the youngest planet yet found by
the main Kepler mission.\footnote{The re-purposed K2
mission however has found two younger systems: K2-33b and V1298 Tau
\citep{David_et_al_2017,Mann_K2_33b_2016,david_four_2019}}  A portion
of the light curve is shown with the phase-folded transit in
Figure~\ref{fig:lc}.  The texttt{PDCSAP}
photometry is dominated by a quasi-periodic starspot signal with a peak-to-peak
amplitude that varies between 2\% and 8\%, depending on the degree of
asymmetry in spot coverage between the stellar hemispheres.  The
starspot signal repeats every $2.642\pm0.042$\,days, where the
uncertainty is based on the scatter observed between different Kepler
quarters.  The details of how we model the starspot signal to derive
the parameters of the planet are discussed in
Appendix~\ref{app:gptransit}.  The stellar parameters are listed in
Table~\ref{tab:starparams}; the stellar mass, radius, and effective
temperature are found by interpolating against a 38$\,$Myr MIST
isochrone.  The systematic uncertainties are taken to be the
difference in parameters from the PARSEC isochrones, and the reported
uncertainties are a quadrature sum of the statistical and systematic
components.  The transit-fitting results, given in
Table~\ref{tab:posterior}, are consistent with a mini-Neptune sized
planet ($3.34\pm 0.18\,R_\oplus$) on a close-in circular\footnote{Our
transit fitting yields $e<0.48$ at 2-$\sigma$; the constraints on the
eccentricity are not particularly strong.} orbit around a G8V star
($0.88 \pm 0.02 R_\odot$).

>>>>

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster using kinematic information from Gaia, stellar rotation
  periods from TESS, and Li abundances from ground-based spectra.  To
  our knowledge, Kepler\,1627Ab is the youngest planet with a precise
  age yet found by the main Kepler mission.  From unresolved
  starspot-crossing events in the Kepler photometry and
  a Keck/HIRES transit we find that the planet is likely on an
  orbit aligned with the stellar spin axis.  We also briefly explore the flare
  arrival time distribution in the short cadence Kepler
  photometry.
  The $\delta$~Lyr cluster is one of many stellar groups whose
  properties have been clarified using the Gaia data; many other new
  clusters also overlap with confirmed and candidate exoplanets.
  Verifying the results of Gaia clustering analyses using TESS rotation
  periods seems likely to be a path toward expanding the census of
  age-dated planets, and our understanding of planetary evolution.
\end{abstract}

@@

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet
\citep[see {\it e.g.},][]{soderblom_ages_2014}.
We acquired an iodine-free spectrum from
Keck/HIRES on the night of 26 March 2021 using the standard setup and
reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we find ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   Note that this value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Given the stellar
parameters of \sn\ (Table~\ref{tab:starparams}), most notably its
effective temperature, this measurement is also in agreement with an
age for the star between 30\,Myr and 50\,Myr ({\it e.g.}, 
\citealt{randich_gaiaeso_2018}; \citealt{bouma_2021_ngc2516}).

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=\textwidth]{f4.pdf}
		}

		\subfloat{
			\includegraphics[width=\textwidth]{f5.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
    30 minute cadence.  A one hundred day segment is shown here.  The
    {\it top panel} shows the \texttt{PDCSAP} median-subtracted flux
    in units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The model for the stellar
    variability (orange line) is subtracted below, revealing the
    transits of \pn, as well as other deviations from the
    model.  The Figure Set online shows the
    entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab, with stellar variability
    removed.  The 2-$\sigma$ model uncertainties and the maximum {\it
    a posteriori} model are shown as the faint purple band, and the
    dark purple line.  Gray points are individual \texttt{PDCSAP} flux
    measurements; black points are binned to 20 minutes, with a
    representative error bar shown.  The asymmetric residual visible
    during the transit is robust against detrending methods; we
    believe it is caused by starspot crossings.
    \label{fig:lc}
  }
\end{figure*}

@@

If the \pn\ transit signal is created by a bonafide planet,  then to
our knowledge its age would make it the youngest planet yet found by
the main Kepler mission.\footnote{The re-purposed K2
mission however has found two younger systems: K2-33b and V1298 Tau
\citep{David_et_al_2017,Mann_K2_33b_2016,david_four_2019}}  A portion
of the light curve is shown with the phase-folded transit in
Figure~\ref{fig:lc}.  The \texttt{PDCSAP}
photometry is dominated by a quasi-periodic starspot signal with a peak-to-peak
amplitude that varies between 2\% and 8\%, depending on the degree of
asymmetry in spot coverage between the stellar hemispheres.  The
starspot signal repeats every $2.642\pm0.042$\,days, where the
uncertainty is based on the scatter observed between different Kepler
quarters.  The details of how we model the starspot signal to derive
the parameters of the planet are discussed in
Appendix~\ref{app:gptransit}.  The stellar parameters are listed in
Table~\ref{tab:starparams}; the stellar mass, radius, and effective
temperature are found by interpolating against a 38$\,$Myr MIST
isochrone.  The systematic uncertainties are taken to be the
difference in parameters from the PARSEC isochrones, and the reported
uncertainties are a quadrature sum of the statistical and systematic
components.  The transit-fitting results, given in
Table~\ref{tab:posterior}, are consistent with a mini-Neptune sized
planet ($3.34\pm 0.18\,R_\oplus$) on a close-in circular\footnote{Our
transit fitting yields $e<0.48$ at 2-$\sigma$; the constraints on the
eccentricity are not particularly strong.} orbit around a G8V star
($0.88 \pm 0.02 R_\odot$).
